Solar jet observed at the limb in SDO/SST

### 2016-05-17 paper/ms_temp_paper.tex
Tiny adjustmetns

Now the temperature profile

>>>>

Essential in investigating jets is their effect on the atmosphere and what occurs at the boundary between jet and atmosphere.
As such, given that the jet is visible in most of the coronal lines we have created temperature maps of the jet and surrounding atmosphere using the method highlighted in \cite{Leonard2014}.
